How fluid-mechanical erosion creates anisotropic porous media

### 2022-06-23 docs/PhysicsPaper/StokesErosion.tex
NM

Rather than tracking the Cartesian coordinates of each surface, we employ the {\thL} formulation \nick{CITE} in which we track the tangent angle $\theta$ as a function of arc length and the total length $L$ of each body.  In this formulation, the curvature-dependent smoothing becomes a linear diffusive term, thus enabling the use of stable, implicit schemes for this stiff term. The remaining nonlinear terms are not stiff and can be treated by explicit time-stepping methods. In particular, we use an exponential integrator for the diffusion term and a Runge-Kutta method for all other terms, both of which are second order in time.

\nick{TO HERE}

>>>>

Rather than tracking the Cartesian coordinates of each surface, we employ the {\thL} formulation \cite{hou-low-she1994, MooreCPAM2017, mac2022morphological} by tracking the tangent angle $\theta$ as a function of arc length and the total length $L$ of each body.  In this formulation, the curvature-dependent smoothing becomes a linear diffusive term, thus enabling the use of stable, implicit schemes for this stiff term. The remaining nonlinear terms are not stiff and can be treated by explicit time-stepping methods. In particular, we use an exponential integrator for the diffusion term and a Runge-Kutta method for all other terms, both of which are second order in time \cite{quaife2018boundary}.
